---
title: "Lab Week 3"
author: "Laurel Abowd"
date: "1/26/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(jtools)
```


```{r}
penguins %>% 
  select(species, bill_length_mm:sex) %>% 
  ggpairs(aes(color = species))
```

Create a subset with only Adelie and Chinstrap penguins. 
```{r}
adelie_chinstrap <- penguins %>% 
  filter(species %in% c("Adelie", "Chinstrap")) %>% 
  mutate(species = fct_drop(species))
```

Let's just dataiz of those two species:
```{r}
ggplot(data = adelie_chinstrap, aes(x = body_mass_g, y 
                                    = flipper_length_mm)) +
  geom_point(aes(color = sex)) +
  facet_wrap(~species)
```

Binary logistic regression 
- body mass
- flipper length 
- penguin sex 

```{r}
adelie_chinstrap_blr <- glm(species~ body_mass_g + flipper_length_mm + sex,
                            data = adelie_chinstrap,
                            family = "binomial" )

```

Take a look at the outcomes:
```{r}
adelie_chinstrap_blr

summary(adelie_chinstrap_blr)
```

Interpret: 
body_mass_g coefficient is -8.57e-04; -> with increase in body mass, odds decrease that it is chinstrap (notice that it is insignificant and small value in magnitude)
flipper_lenght_mm is 1.778; -> increase in flipper length, odds increase that it is chinstrap
sexmale is -5.7 - means that if a penguin is male, is less likely to be chinstrap (doesn't really make sense)

Let's see if the coefficient for flipper_length makes sense looking at data

```{r}
ggplot(data = adelie_chinstrap, aes(x = species, y = flipper_length_mm)) +
  geom_jitter(aes(color = sex))
```

Yes, it looks like chinstraps tends to have longer flippers.

But what are the actual probabilities of being Chinstrap for our variables? 

```{r}
blr_fitted <- adelie_chinstrap_blr %>% 
  broom::augment(type.predict = "response")
```

Plotting fitted probabilities 
```{r}
ggplot(data = blr_fitted, aes(x = flipper_length_mm, y = .fitted)) +
  geom_point(aes(color = sex, pch = species)) +
  geom_smooth(aes(color = sex), se = FALSE) +
  labs(x = "Flipper Length", 
       y = "Probability of outcome is Chinstrap")
```

Can see that some adelie have over a 50% chance of being chinstrap (circles above the 0.50 line)

Plot model based on different variables: 
```{r}
effect_plot(adelie_chinstrap_blr, 
            pred = flipper_length_mm,
            y.label = "Proability of Chinstrap", 
            interval = TRUE)

effect_plot(adelie_chinstrap_blr, 
            pred = body_mass_g,
            y.label = "Proability of Chinstrap", 
            interval = TRUE)
```

What's the probability that a female penguin weighing 3410 g with a flipper length of 192 mm is a Chinstrap? How can I feed these into the model to get a precentage of liklihood?

```{r}
ex_1 <- predict(adelie_chinstrap_blr, 
                data.frame(sex = "female", 
                           body_mass_g = 3410,
                           flipper_length_mm = 192), 
                type = "response")

ex_1

```

Telling us that there is a 40% chance that this is a chinstrap penguin. (have to change it to type = "response" because otherwise we'd get the log odds, which is difficult to understand)
